A multiverse analysis of the associations between internet use and well-being

### 2023-11-13 ms.Rmd
Require Hmisc

library(papaja)
library(scales)
library(knitr)
library(lme4)
library(ggh4x)
library(emmeans)
library(ggside)
library(ggbeeswarm)
library(broom.mixed)
library(patchwork)
library(ggdist)
library(corrr)
library(tidyverse)
opts_chunk$set(
  include = FALSE,
  cache = TRUE
)

>>>>

library(papaja)
library(scales)
library(knitr)
library(lme4)
library(ggh4x)
library(emmeans)
library(ggside)
library(Hmisc)
library(ggbeeswarm)
library(broom.mixed)
library(patchwork)
library(ggdist)
library(corrr)
library(tidyverse)
opts_chunk$set(
  include = FALSE,
  cache = TRUE
)
